
\section{Conclusion and Future Work}

%%Esto lo salvé de otra sección. Habrá que acomodarlo.
We think that our proposal can be applied to other countries around the world who are looking for having a digital ecosystem and better
control over the transaction history that a vehicle can have throughout its life.


%Resumir qué proponemos
In this paper we have proposed a distributed model to store historic transaction record 
about the property of vehicles through blockchain technology. We belief that our proposal
may contribute to extends the paperless culture because might solve the vehicle purchase 
fraud that currently there exists when is only used digital certificate.

%Cuáles son los alcances de lo que proponemos
Our model proposes the creation of a genesis block by the Dealership who has manufactured 
the vehicle and from there, to do different distributed transactions like to sell the vehicle,
change legal status, add important information all of these by different roles of users involved
in the transactions like the owner, government, insurance companies, among others. Doing these, 
a lot of services can be obtained quickly from vehicles for example theft and debt status, different
owners, etc.

Our model involves all participants and how they interact in terms of messages, 
we take care of security aspects in the exchange of messages detailing all the TLS protocol and how it
is connected with the rest of the transaction.

%Decir quién es nuestro universo de nuestra contribución
We belief that our model can be interesting for owners, government, insurance companies, 
vehicle purchase companies or dealerships. Owners always will be grateful having better and 
faster solutions for services. Government could give more and better services. Insurance companies
could have a better estimation about of the price of vehicles. Vehicle purchase companies because
they also have vehicles and they acts as owners at one point.

%Especificar a detalle el Smart Property.
With the dimension that we are proposing, we have some future works:
\begin{itemize}
    \item Specify in detail those functions that are part of the smart property.
    \item Perform the earnings mechanism as done by Ethereum or Bitcoin; and
    \item Develop a prototype: client application with a wallet-vehicle and the
        server side, specifying if all blockchain infrastructure is implemented on 
        Ethereum or create our own blockchain network.
\end{itemize} 
%Formal verification






